TAR System Description Paper Template

### 2017-05-27 paper/paper.tex
tar2017.bib added.

\section{Introduction}

Author diarization is the problem of segmenting text within a document into classes each corresponding to an author, i.e. assignment of each part of a text to an author. The analyzed document can be a result of collaborative work or plagiarism by a single author. The problem is in more detail described here. The problem can be divided into 3 subproblems:
% reference
% authorship analysis, 
% intrinsic plagiarism detection, author diarization
% PAN 2016 author diarization task
% dataset

@@

@@

@@

\bibliographystyle{tar2016}
\bibliography{tar2016}

>>>>

\section{Introduction}
What is the problem ? 
\citep{stein-2011}
Author diarization is the problem of segmenting text within a document into classes each corresponding to an author, i.e. assignment of each part of a text to an author. The analyzed document can be a result of collaborative work or plagiarism by a single author. The problem is in more detail described here. The problem can be divided into 3 subproblems:

% reference
% authorship analysis, 
% intrinsic plagiarism detection, author diarization
% PAN 2016 author diarization task
% dataset

@@

\begin{table}
	\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{cccc}
			\toprule
			Model & $R$ & $P$ & $F_1$\\
			\midrule
			Dummy & 0 & 1 & 2 \\
			One & 0 & 1 & 2 \\
			One & 0 & 1 & 2 \\
			\midrule
			One & 0 & 1 & 2 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}

Mention cofidences.

@@

setup
results

@@

\bibliographystyle{tar2016}
\bibliography{tar2017}
